Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-09-28 manuscript/manuscript.Rmd
reknitted the manuscript.

```{=latex}
\begin{figure}[htp]
\begin{center}
\caption{Regression Model Estimating $\omega$}
```
```{r fig2, out.width = "450px"}
knitr::include_graphics("../figures/figure_2.png")
```
```{=latex}
\end{center}
\footnotesize{\textit{Notes:} The model estimates the proportion of systematic variance attributable to intrapersonal change. It includes the log of the number of participants, the number of waves the variable was asked (capped at t = 10 for each item), the date of the first wave (measured as the year minus 1968 divided by 10), number of waves the question was asked averaged across participants, duration in years per item averaged across participants, and panel and topic fixed effects. Coefficients are estimated from suppressed intercept model based on predictions at participants' wave mid-point. Survey indicators and item topics not shown. See Supplemental Materials B for the full set of coefficients.}
\end{figure}
```

>>>>

```{=latex}
\begin{figure}[htp]
\begin{center}
\caption{Regression Model Estimating $\omega$}
```
```{r fig2, out.width = "350px"}
knitr::include_graphics("../figures/figure_2.png")
```
```{=latex}
\end{center}
\footnotesize{\textit{Notes:} The model estimates the proportion of systematic variance attributable to intrapersonal change. It includes the log of the number of participants, the number of waves the variable was asked (capped at t = 10 for each item), the date of the first wave (measured as the year minus 1968 divided by 10), number of waves the question was asked averaged across participants, duration in years per item averaged across participants, and panel and topic fixed effects. Coefficients are estimated from suppressed intercept model based on predictions at participants' wave mid-point. Survey indicators and item topics not shown. See Supplemental Materials B for the full set of coefficients.}
\end{figure}
```

### 2023-09-28 manuscript/manuscript.tex
reknitted the manuscript.

\begin{document}
\maketitle
\begin{abstract}
Recent work has produced conflicting interpretations on the question of
whether adults undergo durable changes in their personal culture over
time. This paper asserts that this divergence is less due to
researchers' findings than the approach taken -- a tournament of models
focusing on the presence or absence of change. To move beyond this, we
reanalyze the data used previously in this debate with an approach that
quantifies the processes of cultural difference. In doing so, we compare
how much cultural difference is explained by intrapersonal change and
interpersonal differences. Our results harmonize recent findings by
showing that, while most measures of personal culture show change over
time, the variance explained by intrapersonal change is typically small
compared to interpersonal differences at baseline. Quantifying these
processes offers new ways to address theoretical questions of when and
how their relative importance shifts. We examplify this approach by
exploring how the importance of these processes differs between college
graduates and the rest of the population.
\end{abstract}

@@

These seemingly inconsistent findings are partly due to the fact that
researchers have taken a ``tournament of models'' approach to
adjudicating different theoretical perspectives (Lersch 2023: p.~228).
That is, researchers have compared the fit of different statistical
models to each item to determine whether it is more consistent with ``no
change'' or ``any change.'' The size of these piles then serves as the
primary evidence for the truth of the theory (Kiley and Vaisey 2020;
Lersch 2023; Vaisey and Kiley 2021).

We argue, however, that asking \emph{whether} people change on an item
may cause more problems than it solves. Being able to detect \emph{any}
change on an item depends not only on sample populations, measurement,
statistical methods, and power, but also on definitions of what counts
as ``change.'' These differences can limit the possibility of agreement
on which ``pile'' a variable belongs in. Moreover, asking whether there
is evidence of change reduces to, ``Is there \emph{any} evidence of
change in this item?'' But such binary inquiries are ill-suited to
address the core of the theoretical debate: determining \emph{how much}
the process of intrapersonal change contributes to cultural differences.

There is enough evidence to assert that neither pre-adult socialization
nor the contemporary social context alone can explain the full range of
cultural differences. The question that remains is about the
\emph{relative} contributions of these processes. In the current debate,
for a single construct (e.g., support for gay rights), existing
approaches can only make claims about \emph{whether} intrapersonal
change is happening, not about how much. This also prevents
investigating under what conditions, across which groups, and in what
domains do we see differences in the relative importance of
intrapersonal change and pre-existing interpersonal differences. These
questions are about \emph{degree}, not existence; taking this debate
forward will require precise measurement rather than declarations of
victory for a particular perspective.

@@

Taken together, to goal of this paper is to advance---and, hopefully,
transcend---debates about \emph{whether} adults change. People do
change, at least a little, on most things. Our method can help quantify
exactly how much.

@@

Despite differences in how these researchers interpret their findings,
the empirical results are not far apart. Kiley and Vaisey (2020) found
that the majority of items they tested favored the AUM, meaning there
was evidence of durable change among adults, a pattern consistent with
Lersch's results. While Lersch (2023) found evidence of durable change
on most items, this change only accounted for a small proportion of
variance explained. On average, people changed only about .07 standard
deviations over 10 years. This is consistent with Kiley and Vaisey's
finding that durable change is often small. And a quarter of the items
Lersch studied still preferred the SDM, suggesting that even with
different assumptions assumptions about change and more extensive data,
many questions show no evidence of durable change. Likewise, in studies
showing evidence of durable change in specific measures of personal
culture, the change is often small. For example, Brocic and Miles (2021)
estimate that completing graduate degrees in humanities, arts, and
social sciences shift peoples' moral relativism only about .2 standard
deviations on average compared to people with no college degree, and
this is the largest effect they identify. And studies of aggregate
change show that, even on items where cohort effects explain more
variance than period effects, there is always evidence that some people
change over time (Vaisey and Lizardo 2016). In other words, despite
different interpretations, the results of previous work are in many ways
highly consonant.

@@

In this approach, there are two metrics that each reflect a combination
of relevant theoretical processes. The first metric, interpersonal
differences at the start of the survey, reflects the accumulated
experiences of people prior to entering the panel survey that shape how
they answer questions. Lersch calls this ``early imprinting.'' While
commonly associated with experiences during a formative period that
result in settled dispositions, this variation could also reflect
experiences that happen at any stage in life as long as they predate the
panel and consistently affect subsequent responses. For instance, for
those people entering the panel post-retirement, this ``imprinting''
might reflect this pivotal life transition. Consequently, this metric
also reflects variation in individuals' social roles or statuses at the
start of the panel that were important in shaping their dispositions.

@@

A third metric, often called ``residual variance'' or ``fluctuation,''
accounts for the remainder of variance in peoples' responses. This
non-durable change emerges for a variety of reasons. For example, people
might not have clear a clear disposition on a particular item as it is
asked. Instead, they might internalize a broad set of considerations and
construct an opinion in the context of the survey interview, with
different considerations coming to the forefront of their cognition each
interview (Feldman and Zaller 1992; Tourangeau, Rips, and Rasinski 2000;
Zaller 1992). Additionally, this variance can also include measurement
error, such as misinterpreted questions, erroneous response selections,
or responses getting coded incorrectly. While this third metric at least
partially reflects important processes of personal culture, it does not
directly touch on the ongoing debate outlined here. Because of this we
quantify this component but focus principally on the other two.

@@

We use data from 7 nationally representative panel surveys from
Australia, Germany, Great Britain, Switzerland, and the United States
(summarized in Table 1), combining all the data files used in previous
work (Kiley and Vaisey 2020; Lersch 2023).\footnote{For more information
  on these data sources, see (Goebel et al. 2019; Income Dynamics 2013;
  Smith et al. 2022; Summerfield et al. 2011; Taylor 1996; University of
  Essex and Research 2019; Voorpostel et al. 2016).} These studies cover
a long period of time (the range of surveys spans from 1968 to 2021),
with 609 personal culture items that capture attitudes, beliefs, values,
self-assessments, self-descriptions, and behaviors (Alwin 2007). We
restricted the sample such that individuals between the ages of 18 and
79 are included without further elimination, and in all surveys, we used
all possible cases for which respondents provided responses. In the end,
the analyses that follow rely on a cross-cultural sample with a
cross-domain set of items to capture a broad range of individual
personal culture. Supplemental Materials A documents the list of all
variables used in the upcoming analyses.

@@

We can think of this number, \(\omega\) as akin to an Intraclass
Correlation Coefficient focused only on the systematic components of the
model while ignoring residual variance that might be attributable to
measurement error or non-persisting change (see also the variance
decomposition of period and cohort by Vaisey and Lizardo 2016). The
higher this number is, the more systematic variance in responses is
attributable to intrapersonal change during the panel. The lower the
number, the less intrapersonal change seems to play a large role in
explaining systematic cultural differences during the panel. Moving
forward, we use \(\omega\) as a placeholder for \emph{systematic
variance attributable to intrapersonal change}.

@@

As a second step in our analysis, we use ordinary least squares
regression to model \(\omega\) as a function of features of the question
and panel. This allows us to explore how these features affect the
prevalence of intrapersonal change. These covariates include the number
of response options (measured as 2, 3-5, and more than 5), the panel,
the log of the number of participants, the number of waves observed, the
time since the question was first asked, and the total span of time the
question was asked.

@@

Figure 1 plots the proportion of systematic variance attributable to
interpersonal differences and intrapersonal change for each of the 609
questions analyzed, plotted separately by panel. To broadly summarize
the results, all panels show a similar range of the proportion of
systematic variance attributable to intrapersonal change. Across panels,
the median proportion of \(\omega\) is 0.094 (mean of 0.098), with an
interquartile range of 0.053 to 0.139. All panels include questions
where \(\omega\) is essentially 0, and all panels include questions with
\(\omega\) values greater than 0.20. The maximum \(\omega\) value is
0.26.

@@

In contrast to the tournament of models approach, quantifying change
this way allows us to explore variation in the relative importance of
intrapersonal change across questions that all both show evidence of
change. For example, Kiley and Vaisey (2020) found that confidence in
the press and confidence in religious leaders were both characterized by
active updating. Our results show that intrapersonal change is much more
important for explaining variance in confidence in the press (0.164)
than confidence in religion (0.049).

@@

\includegraphics[width=450px]{../figures/figure_2}

@@

Figure 2 shows that the more response options respondents are given and
the larger the sample, the larger the values of \(\omega\). We interpret
these coefficients as suggesting greater resolution on a question makes
it easier to detect and model change. The earlier a question was asked,
even net of how long it was been asked, the lower the \(\omega\).

While we did not generate expectations for how question content relates
to \(\omega\), some of the associations between question structure,
panel duration, and panels themselves might be driven by differences in
the topics addressed by each panel. To address this, we coded each
question as falling into one of nine different content categories and
included these as indicator variables in the meta analysis. Supplemental
Materials B presents the estimates for these content indicators. They
show some associations with \(\omega\), with questions about subjective
SES; social life, social cohesion, and trust; environment and climate;
and health and morale showing larger \(\omega\) values than questions
about religion and spirituality; politics, government and the economy;
and gender and family.

@@

On all eight questions presented in Figure 4, \(\omega\) values are
greater for people without a college degree than for people with a
college degree, meaning intrapersonal change explains less systematic
variance for people with a college degree than for people without one.
There are also large differences in \(\omega\) values across questions
for both groups. For example, on the question of whether the government
should try to solve more problems or leave those problems to be solved
by private businesses (``government do more or less''), less than one
percent of the systematic variance is attributable to intrapersonal
change for both groups. In other words, while people might vacillate on
this question at random (37 percent of variance is residual for this
question), there is functionally no evidence that people make systematic
changes of opinion on this issue during the GSS panel.

@@

This conclusion aligns with a range of recent causal inference work
suggesting that selection effects, rather than treatment effects,
predominantly account for personal cultural differences among
individuals in varied social roles and positions (Campbell and Horowitz
2016; Wodtke 2018). While some people clearly change as they transition
into new roles or environments, this change often seems to be
insufficient in magnitude and duration to explain what are often
pronounced differences among people in diverse roles. These and our
results suggest that when observing differences in personal culture
across social roles, such as parenthood, education, or professional
authority (Longest, Hitlin, and Vaisey 2013), or across occupations
(Weeden and Grusky 2005), selection likely plays a large role in
explaining these difference, though exceptions always exist.

@@

Further, we align with others {[}\textbf{WE NEED SOME CITES HERE}{]}
advocating for more studies --including panel studies-- focusing on the
socialization of youth. Our analysis points to the majority of variance
among adults rooting in differences encountered before turning 18. By
empirically constraining their analysis to experiences after that point,
social scientists may inadvertently concentrate on topics and questions
that, while important, might not be able to help explain major cultural
differences in adult populations.

Finally, a key insight from our meta-analysis is that an increase in
response resolution --the range of response options survey respondents
are given-- correlates with an increased share of systematic variance
explained by intrapersonal change. This may reflect specific issues
being assessed by survey items using different scales. Alternatively, it
might imply that when intrapersonal changes occurs, they are often
subtle with answers moving from ``agree'' to ``strongly agree,'' rather
than from ``strongly agree'' to ``strongly disagree.'' Such subtle
changes require finer response options to be detected.

@@

Similarly, our approach assumes that durable change is unidirectional.
This is a sensible assumption on short panels where classifying change
that lasts less than two years as durable seems unreasonable.
Practically, it means that the variance produced by people making
durable changes in their cultural dispositions to then returning to a
previous state later in life is classified as residual variance, rather
than intrapersonal change. Longer panels and more flexible definitions
of ``change'' would allow us to account for such trajectories and thus
potentially also identify more durable change even in the same
population.

@@

>>>>

\begin{document}
\maketitle
\begin{abstract}
Recent work has produced conflicting interpretations on the question of
whether adults undergo durable changes in their personal culture over
time. This paper asserts that this divergence is less due to
researchers' findings than the approach taken -- a tournament of models
focusing on the presence or absence of change. To move beyond this, we
reanalyze the data used previously in this debate with an approach that
quantifies the processes of cultural difference. In doing so, we compare
how much cultural difference is explained by intrapersonal change and
interpersonal differences. Our results harmonize recent findings by
showing that, while most measures of personal culture show durable
change over time, the variance explained by intrapersonal change is
typically small compared to that of interpersonal differences at
baseline. Quantifying these processes offers new ways to address
theoretical questions of when and how their relative importance shifts.
We exemplify this approach by exploring how the importance of these
processes differs between college graduates and the rest of the
population.
\end{abstract}

@@

These seemingly inconsistent findings are partly due to the fact that
researchers have taken a ``tournament of models'' approach to adjudicate
different theoretical perspectives (Lersch 2023: p.~228). That is,
researchers have compared the fit of different statistical models to
each item to determine whether it is more consistent with ``no change''
or ``any change.'' The size of these piles then serves as the primary
evidence for the truth of the theory (Kiley and Vaisey 2020; Lersch
2023; Vaisey and Kiley 2021).

We argue, however, that asking \emph{whether} people change on an item
may cause more problems than it solves. Being able to detect \emph{any}
change on an item depends not only on sample populations, measurement,
statistical methods, and power, but also on definitions of what counts
as ``change.'' These differences can limit the possibility of agreement
on which ``pile'' a variable belongs. Moreover, asking whether there is
evidence of change reduces to, ``Is there \emph{any} evidence of change
in this item?'' But such binary inquiries are ill-suited to address the
core of the theoretical debate: determining \emph{how much} the process
of intrapersonal change contributes to cultural differences.

There is enough evidence to assert that neither pre-adult socialization
nor the contemporary social context alone can explain the full range of
cultural differences. The question that remains is about the
\emph{relative} contributions of these processes. In the current debate,
for a single construct (e.g., support for gay rights), existing
approaches can only make claims about \emph{whether} intrapersonal
change is happening, not about how much. This also prevents
investigating under what conditions, across which groups, and in what
domains do we see differences in the relative importance of
intrapersonal change and pre-existing interpersonal differences. These
questions are about \emph{degree}, not existence; to take this debate
forward therefore requires precise measurement rather than declarations
of victory for a particular perspective.

@@

Taken together, the goal of this paper is to advance---and, hopefully,
transcend---debates about \emph{whether} adults change. People do
change, at least a little, on most things. Our method can help quantify
exactly \emph{how much}.

@@

Despite differences in how these researchers interpret their findings,
the empirical results are not far apart. Kiley and Vaisey (2020) found
that the majority of items they tested favored the AUM, meaning there
was evidence of durable change among adults, a pattern consistent with
Lersch's results. Also Lersch (2023) found evidence of durable change on
most items, but this change only accounted for a small proportion of
variance explained. On average, people changed only about .07 standard
deviations over 10 years. This is consistent with Kiley and Vaisey's
finding that durable change is often small. Moreover, a quarter of the
items Lersch studied still preferred the SDM, suggesting that even with
different assumptions assumptions about change and more extensive data,
many questions show no evidence of durable change. Consistent with this,
in studies showing evidence of durable change in specific measures of
personal culture, the change is often small. For example, Brocic and
Miles (2021) estimate that completing graduate degrees in humanities,
arts, and social sciences shift peoples' moral relativism only about .2
standard deviations on average compared to people with no college
degree, and this is the largest effect they identify. And studies of
aggregate change show that, even on items where cohort effects explain
more variance than period effects, there is always evidence that some
people change over time (Vaisey and Lizardo 2016). In other words,
despite different interpretations, the results of previous work are in
many ways highly consonant.

@@

We propose an approach that offers such a quantification. In this
approach, there are two metrics that each reflect a combination of
relevant theoretical processes. The first metric, interpersonal
differences at the start of the survey, reflects the accumulated
experiences of people prior to entering the panel survey that shape how
they answer questions. Lersch calls this ``early imprinting.'' While
commonly associated with experiences during a formative period that
result in settled dispositions, this variation could also reflect
experiences that happened at any stage in life as long as they predate
the panel and consistently affect subsequent responses. For instance,
for those people entering the panel post-retirement, this ``imprinting''
might reflect this pivotal life transition. Consequently, this metric
also reflects variation in individuals' social roles or statuses at the
start of the panel that were important in shaping their dispositions.

@@

A third metric, often called ``residual variance'' or ``fluctuation,''
accounts for the remainder of variance in peoples' responses. This
non-durable change emerges for a variety of reasons. For example, people
might not have a clear disposition on a particular item as it is asked.
Instead, they might internalize a broad set of considerations and
construct an opinion in the context of the survey interview, with
different considerations coming to the forefront of their cognition
during each interview (Feldman and Zaller 1992; Tourangeau, Rips, and
Rasinski 2000; Zaller 1992). Additionally, this variance can also
include measurement error, such as misinterpreted questions, erroneous
response selections, or responses getting coded incorrectly. While this
third metric at least partially reflects important processes of personal
culture, it does not directly touch on the ongoing debate outlined here.
Because of this we quantify this component but focus principally on the
other two.

@@

We use data from seven nationally representative panel surveys from
Australia, Germany, Great Britain, Switzerland, and the United States
(summarized in Table 1), combining all the data files used in previous
work (Kiley and Vaisey 2020; Lersch 2023).\footnote{For more information
  on these data sources, see (Goebel et al. 2019; Income Dynamics 2013;
  Smith et al. 2022; Summerfield et al. 2011; Taylor 1996; University of
  Essex and Research 2019; Voorpostel et al. 2016).} These studies cover
a long period of time (the range of surveys spans from 1968 to 2021),
with 609 personal culture items that capture attitudes, beliefs, values,
self-assessments, self-descriptions, and behaviors (Alwin 2007). We
restricted the sample such that individuals between the ages of 18 and
79 are included without further elimination, and in all surveys, we used
all possible cases for which respondents provided responses. In the end,
the analyses that follow rely on a cross-cultural sample with a
cross-domain set of items to capture a broad range of individual
personal culture. Supplemental Materials A documents the list of all
variables used in the upcoming analyses.

@@

We can think of this proportion \(\omega\) as akin to an Intraclass
Correlation Coefficient focused only on the systematic components of the
model while ignoring residual variance that might be attributable to
measurement error or non-persisting change (see also the variance
decomposition of period and cohort by Vaisey and Lizardo 2016). The
higher this proportion is, the more systematic variance in responses is
attributable to intrapersonal change during the panel. The lower this
proportion, the less intrapersonal change seems to play a large role in
explaining systematic cultural differences during the panel. Moving
forward, we use \(\omega\) as a placeholder for \emph{systematic
variance attributable to intrapersonal change}.

@@

As a second step in our analysis, we use ordinary least squares
regression to model \(\omega\) as a function of features of the question
and panel. This allows us to explore how these features affect the
prevalence of intrapersonal change. These covariates include the number
of response options (measured as 2, 3-5, and more than 5), the panel,
the log of the number of participants, the number of waves observed, the
time since the question was first asked, and the total duration of time
the question was asked.

@@

Figure 1 plots the proportion of systematic variance attributable to
interpersonal differences and intrapersonal change for each of the 609
questions analyzed, plotted separately by panel. To broadly summarize
the results, all panels show a similar range of the proportion of
systematic variance attributable to intrapersonal change. Across panels,
the median value of \(\omega\) is 0.094 (mean of 0.098), with an
interquartile range of 0.053 to 0.139. All panels include questions
where \(\omega\) is essentially 0, and all panels include questions with
\(\omega\) values greater than 0.20. The maximum \(\omega\) value is
0.26.

@@

In contrast to the tournament of models approach, quantifying change
this way allows us to explore variation in the relative importance of
intrapersonal change across questions that all show evidence of change.
For example, Kiley and Vaisey (2020) found that confidence in the press
and confidence in religious leaders were both characterized by active
updating. Our results show that intrapersonal change is much more
important for explaining variance in confidence in the press (0.164)
than confidence in religion (0.049).

@@

\includegraphics[width=350px]{../figures/figure_2}

@@

Figure 2 shows that the more response options respondents are given and
the larger the sample, the larger the values of \(\omega\). We interpret
these coefficients as suggesting greater resolution on a question makes
it easier to detect and model change. The earlier a question was asked,
even net of how long it was been asked, the lower \(\omega\).

While we did not generate expectations for how question content relates
to \(\omega\), some of the associations between question structure,
panel duration, and panels themselves might be driven by differences in
the topics addressed by each panel. To address this, we followed Hout et
al. (2016) and Lersch (2023) in coding each question as falling into one
of nine different content categories and included these as indicator
variables in the meta analysis. Supplemental Materials B presents the
estimates for these content indicators. They show some associations with
\(\omega\), with questions about subjective SES; social life, social
cohesion, and trust; environment and climate; and health and morale
showing larger \(\omega\) values than questions about religion and
spirituality; politics, government and the economy; and gender and
family.

@@

On all eight questions presented in Figure 4, \(\omega\) values are
smaller for people with a college degree than for people without a
college degree, meaning intrapersonal change explains less systematic
variance for people with a college degree than for people without one.
There are also large differences in \(\omega\) values across questions
for both groups. For example, on the question of whether the government
should try to solve more problems or leave those problems to be solved
by private businesses (``government do more or less''), less than one
percent of the systematic variance is attributable to intrapersonal
change for both groups. In other words, while people might vacillate on
this question at random (37 percent of variance is residual for this
question), there is functionally no evidence that people make systematic
changes of opinion on this issue during the GSS panel.

@@

This conclusion aligns with a range of recent causal inference work
suggesting that selection effects, rather than treatment effects,
predominantly account for personal cultural differences among
individuals in varied social roles and positions (Campbell and Horowitz
2016; Wodtke 2018). While some people clearly change as they transition
into new roles or environments, this change seems to be insufficient in
magnitude and duration to explain what are often pronounced differences
among people in diverse roles. These and our results suggest that when
observing differences in personal culture across social roles, such as
parenthood, education, or professional authority (Longest, Hitlin, and
Vaisey 2013), or across occupations (Weeden and Grusky 2005), selection
likely plays a large role in explaining these difference, though
exceptions always exist.

@@

Further, we align with others {[}\textbf{WE NEED SOME CITES HERE}{]}
advocating for more studies, including panel studies, focusing on the
socialization of youth. Our analysis points to the majority of variance
among adults rooting in differences encountered before turning 18. By
empirically constraining their analysis to experiences after that point,
social scientists may inadvertently concentrate on topics and questions
that, while important, might not be able to help explain major cultural
differences in adult populations.

Finally, a key insight from our meta-analysis is that an increase in
response resolution (the range of response options survey respondents
are given) correlates with an increased share of systematic variance
explained by intrapersonal change. This may reflect specific issues
being assessed by survey items using different scales. Alternatively, it
might imply that when intrapersonal changes occurs, they are often
subtle with answers moving from ``agree'' to ``strongly agree,'' rather
than from ``strongly agree'' to ``strongly disagree.'' Such subtle
changes require finer response options to be detected.

@@

Similarly, our approach assumes that durable change is unidirectional.
This is a sensible assumption on short panels where classifying change
that lasts less than two years as durable seems unreasonable.
Practically, it means that the variance produced by people making
durable changes in their cultural dispositions to then return to a
previous state later in life is classified as residual variance, rather
than intrapersonal change. Longer panels and more flexible definitions
of ``change'' would allow us to account for such trajectories and thus
potentially also identify more durable change even in the same
population.

@@

\leavevmode\vadjust pre{\hypertarget{ref-hout2016}{}}%
Hout, Michael, and Orestes P. Hastings. 2016. {``Reliability of the
{Core} {Items} in the {General} {Social} {Survey}: {Estimates} from the
{Three}-{Wave} {Panels}, 2006--2014.''} \emph{Sociological Science}
3:971--1002. doi:
\href{https://doi.org/10.15195/v3.a43}{10.15195/v3.a43}.
